\documentclass[a4paper,20pt]{report}
\begin{document}
\title{HOW TO SECRETELY BUY KIKOMANDO WITHOUT BEING NOTICED BY ANY ONE:}
\author{KATUMBA HENRY 15/U/403}


\date{30/3/2017}

\maketitle

\subsection{SUMMARY}
\paragraph{My research is about identifying the customers around kikomando places and mostly around campus hostels through observations and experimentations. }
\paragraph{Customers always with bags, polythene papers, smart phones and those resting near or close to places selling kikomando form a good group to aid my research.}

\section{INTRODUCTION}

\subparagraph{This report is mainly about how one can buy a kikomando in secrete without being noticed by any one.}
\subparagraph{Kikomando is chapatti mixed commonly with beans source and rarely it could be meat source, peas and ground nuts. It is commonly sold around campus hostels thus commonly bought by students but other people also buy it.}
\subparagraph{Customers are those people who buy the kikomando.}

\subsection{METHODOLOGY}
\subsection{I collected the information through,}
\begin {enumerate}
\item-experimentally buying the kikomando myself secretly 
\item -observing the students and other people do the same.
\end{enumerate}

I used the following tools to record all the information i collected from the kikomando sellers
\begin {enumerate}

\item pens.
\item book.
\end {enumerate}
\subsection{FINDINGS}
\subsection{based on all the research i did, i concluded the following.}
\begin{enumerate}
\item{The daily customers usually buy the kikomando on hot sunny or evening when people cannot take clear focus on them and always in the evening when it’s getting dark such that they cannot be noticed by anyone.}
\item{These daily customers are ever with smart phones pretending to be chatting while the kikomando seller is busy packing for them.}
\item{They carry bags or colored polythene papers in which to place it after it is packed.}
\item{They carry packed kikomando home or on rare occasions eat from where they buy it while sitting in the corners to They avoid being noticed.}
\end{enumerate}

\subsection{REFERENCES}
Author = MUNA OMUSOGA the kikomando seller
location= {KIKONI AROUND KASUBI MARKET}




\end{document}
